---
title: "Lesson 6"
author: "Xiaoni"
date: "4/1/2020"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Quiz 1.price vs. x

```{r price vs. x}
# In this problem set, you'll continue
# to explore the diamonds data set.

# Your first task is to create a
# scatterplot of price vs x.
# using the ggplot syntax.

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ===========================================
library(ggplot2)
data(diamonds)
names(diamonds)

ggplot(aes(x = x, y = price), data = diamonds) +
  geom_point()
ggsave('PriceX1.png')

ggplot(aes(x = x, y = price), data = diamonds) +
  geom_point() +
  scale_x_log10() +

ggsave('PriceX2.png')

```

# Quiz 2. Findings - price vs. x

What are your observations about the scatterlot of price vs. x?
Response: It looks like that there are some outliers and an exponential relationship between price and x.

# Quiz 3. Correlations
1.What is the correlation between price and x?
Response:0.88
2.What is the correlation between price and y?
Response:0.87
3. What is the correlation between price and z?
Response:0.86
```{r Correlations}
with(diamonds, cor(price, x))
with(diamonds, cor(price, y))
with(diamonds, cor(price, z))

```

#Quiz 4. price vs. depth

```{r price vs. depth}
# Create a simple scatter plot of price vs depth.

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
#==================================================
ggplot(aes(x = depth, y = price), data = diamonds) + 
  geom_point()
ggsave('Pricedepth.png')
```

#Quiz 5. Adjustments - price vs. depth

```{r Adjustments - price vs. depth}
# Change the code to make the transparency of the
# points to be 1/100 of what they are now and mark
# the x-axis every 2 units. See the instructor notes
# for two hints.

# This assignment is not graded and
# will be marked as correct when you submit.

# ALTER THE CODE BELOW THIS LINE
#============================================
ggplot(data = diamonds, aes(x = depth, y = price)) + 
  geom_point(alpha = 1/100) +
  scale_x_continuous(breaks = seq(0, 18830, 2))
ggsave('PricedepthAdj.png')
```

# Quiz 6. Typical Depth Range
Base on the sactterplot of depth vs. price,most diamonds are between what values of depth?
Reponse:58-64

```{r Typical Depth Range}
summary(diamonds$depth)
```

# Quiz 7. Correlation - price and depth
1. What's the correlation between depth vs. price?
Response: -0.01
2. Base on the correation coefficient would you use depth to preict the price of diamonds?
Response: No
3. Why?
Response: R value is around 0.

```{r Correlation - price and depth}
with(diamonds, cor.test(depth, price, method = 'pearson'))
```

# Quiz 8.price vs. carat

```{r price vs. carat}
# Create a scatterplot of price vs carat
# and omit the top 1% of price and carat
# values.

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ========================================
ggplot(aes(x = carat, y = price), data = diamonds) +
  geom_point() +
  xlim(0, quantile(diamonds$carat, 0.99)) +
  ylim(0, quantile(diamonds$price, 0.99))

ggsave('0.95priceCarat.png')

```

# Quiz 9.price vs. volume

```{r price vs. volume}
# Create a scatterplot of price vs. volume (x * y * z).
# This is a very rough approximation for a diamond's volume.

# Create a new variable for volume in the diamonds data frame.
# This will be useful in a later exercise.

# Don't make any adjustments to the plot just yet.

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# =================================================================
diamonds$volume = diamonds$x * diamonds$y * diamonds$z

ggplot(aes(x = volume, y = price), data = diamonds) +
  geom_point()
ggsave('Pricevolume1.png')

ggplot(aes(x = volume, y = price), data = diamonds) +
  geom_point() +
  scale_x_log10()
ggsave('Pricevolume2.png')

```
# Quiz 10.Findings - price vs. volume
What are your observations about the scatterlot of price vs. volume scatterplot?
Response: It looks like that there are some outliers and an exponential relationship between price and volume.

```{r Findings - price vs. volume}
library(plyr)
count(diamonds$volume == 0)

```
# Quiz 11. Correlations on Subsets
What's the correlation of price and volume? Exclude diamonds that have a volume of 0 or that are greater than or equal to 800.
Response: 0.9235455 
 
```{r Correlations on Subsets}
with(subset(diamonds, diamonds$volume < 800 & diamonds$volume > 0), 
     cor.test(volume, price))
```
# Quiz 12.Adjustments - price vs. volume
Do you think this would be a useful model to estimate the price of diamonds? 
Why or why not?
Response: Yes. Because cor value is almost 1.

```{r Adjustments - price vs. volume}
# Subset the data to exclude diamonds with a volume
# greater than or equal to 800. Also, exclude diamonds
# with a volume of 0. 

# Adjust the transparency of the points and add a 
# linear model to the plot. (See the
# Instructor Notes or look up the documentation of
# geom_smooth() for more details about smoothers.)

# We encourage you to think about this next question and
# to post your thoughts in the discussion section.

# Do you think this would be a useful model to estimate
# the price of diamonds? Why or why not?

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ========================================

ggplot(aes(x = volume, y = price), data = subset(diamonds, diamonds$volume < 800 & diamonds$volume > 0)) +
  geom_point() +
  stat_smooth(method = "lm", formula = y ~ x, color = 'red',size = 1)
ggsave('smooth1.png')

```

#Quiz 13. Mean Price by Clarity
```{r Mean Price by Clarity}
# Use the function dplyr package
# to create a new data frame containing
# info on diamonds by clarity.

# Name the data frame diamondsByClarity

# The data frame should contain the following
# variables in this order.

#       (1) mean_price
#       (2) median_price
#       (3) min_price
#       (4) max_price
#       (5) n

# where n is the number of diamonds in each
# level of clarity.

# This assignment WILL BE automatically
# graded!

# DO NOT ALTER THE NEXT THREE LINES OF CODE.
# ======================================================
suppressMessages(library(ggplot2))
suppressMessages(library(dplyr))
#data(diamonds)

# ENTER YOUR CODE BELOW THIS LINE
# ======================================================
#uninstall package(plyr)
#detach("package:plyr", unload=TRUE)

diamondsByClarity = diamonds %>%
  group_by(clarity) %>%
  summarise(mean_price = mean(price),
            median_price = median(price),
            min_price = min(price),
            max_price = max(price),
            count = n()) %>%
  arrange(clarity)


```

# Quiz 14. Bar Charts of Mean Price
```{r Bar Charts of Mean Price}
# We’ve created summary data frames with the mean price
# by clarity and color. You can run the code in R to
# verify what data is in the variables diamonds_mp_by_clarity
# and diamonds_mp_by_color.

# Your task is to write additional code to create two bar plots
# on one output image using the grid.arrange() function from the package
# gridExtra.

# This assignment is not graded and
# will be marked as correct when you submit.

# See the Instructor Notes for more info on bar charts
# and for a hint on this task.

# DO NOT DELETE THE LINES OF CODE BELOW
# ===================================================================
# data(diamonds)
# library(dplyr)

diamonds_by_clarity <- group_by(diamonds, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- summarise(diamonds_by_color, mean_price = mean(price))

# ENTER YOUR CODE BELOW THIS LINE
# ===================================================================

library(ggplot2)
head(diamonds_by_clarity)
head(diamonds_mp_by_clarity)
head(diamonds_by_color)
head(diamonds_mp_by_color)

pbar1 = ggplot(aes(x = mean_price, y= clarity), data = diamonds_mp_by_clarity) + 
  stat_summary(fun = mean, geom = "bar")
pbar2 = ggplot(aes(x = mean_price, y= color), data = diamonds_mp_by_color) + 
  stat_summary(fun = mean, geom = "bar")

library(gridExtra)
grid.arrange(pbar1,pbar2, ncol = 1)
ggsave('bar12.png')

```

# Quiz 15. Trends in Mean Price
What do you notice in each of bar charts for mean price by clarity and mean price by color?
Response: 
1. According to the difine of clarity, a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best)).However, mean price tends to decrease as clarity improves.

#Quiz 16.Gapminder Revisited
```{r Gapminder Revisited}
# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to continue the investigation you did at the
# end of Problem Set 3 or you can start fresh and choose a different
# data set from Gapminder.

# If you’re feeling adventurous or want to try some data munging see if you can
# find a data set or scrape one from the web.

# In your investigation, examine pairs of variable and create 2-5 plots that make
# use of the techniques from Lesson 4.

# You can find a link to the Gapminder website in the Instructor Notes.

# Once you've completed your investigation, create a post in the discussions that includes:
#       1. the variable(s) you investigated, your observations, and any summary statistics
#       2. snippets of code that created the plots
#       3. links to the images of your plots

# Copy and paste all of the code that you used for
# your investigation, and submit it when you are ready.
# ====================================================================
babies = read.csv('children_per_woman_total_fertility.csv')
names(babies)
head(babies,8)
library(ggplot2)
ggplot(aes(x = country, y = X1900), data = babies) + 
  geom_point()

ggsave('point1.png')
summary(babies$X1800)
range(babies$X1900)


library(dplyr)
babies.X1900_by_country = babies %>%
  group_by(country) %>%
  summarise(X1900_mean = mean(X1900),
           X1900_median = median(X1900),
           n = n()) %>%
  arrange(country)

ggplot(aes(x = country, y = X1900_mean), data = babies.X1900_by_country) +
  geom_point() 
ggsave('point2.png')

ggplot(aes(x = X1800, y = X1900), data = babies) +
  geom_line() +
  geom_smooth()
ggsave('line.png')

with(babies, cor.test(X1800, X1900))


```




When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 