---
output:
  pdf_document: default
  html_document: default
---
Lesson 5
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf=read.csv('pseudo_facebook.tsv', sep = '\t')

qplot(x = age, y = friend_count, data = pf)
ggsave('scatter1.png')

qplot(age, friend_count, data = pf)
ggsave('scatter2.png')
```

***

#### What are some things that you notice right away?
Response:
range around25, much more friend_count.
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + geom_point() +
  xlim(13, 90)

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:
1. friend_count of more younger is below 1000;
2. y-axis is not suitable.
***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha=1/20) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha=1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt")
```

#### What do you notice?

***
The density for the left corner is much higher.


### Alpha and Jitter
Notes:

```{r Alpha and Jitter}

# Examine the relationship between
# friendships_initiated (y) and age (x)
# using the ggplot syntax.

# We recommend creating a basic scatter
# plot first to see what the distribution looks like.
# and then adjusting it by adding one layer at a time.

# What are your observations about your final plot?

# Remember to make adjustments to the breaks
# of the x-axis and to use apply alpha and jitter.

# ENTER ALL OF YOUR CODE FOR YOUR PLOT BELOW THIS LINE.
# =======================================================
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha=1/20, position = position_jitter(h=0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")

summary(pf$friendships_initiated)


```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
#install.packages("dplyr")
library(dplyr)
age_groups = group_by(pf, age)
pf.fc_by_age = summarise(age_groups, 
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n())
pf.fc_by_age = arrange(pf.fc_by_age, age)
head(pf.fc_by_age)

```

Create your plot!

```{r Conditional Means Plot}
library(dplyr)
pf.fc_by_age = pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
           friend_count_median = median(friend_count),
           n = n()) %>%
  arrange(age)

head(pf.fc_by_age,15)


# Plot mean friend count vs. age using a line graph.
# Be sure you use the correct variable names
# and the correct data frame. You should be working
# with the new data frame created from the dplyr
# functions. The data frame is called 'pf.fc_by_age'.

# Use geom_line() rather than geom_point to create
# the plot. You can look up the documentation for
# geom_line() to see what it does.

# ENTER ALL OF YOUR CODE TO CREATE THE PLOT BELOW THIS LINE.
# ===========================================================
library(ggplot2)
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) +
  geom_line()

```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
library(dplyr)
library(Lahman)
ggplot(aes(x = age, y = friend_count), data = pf) +
  coord_cartesian(xlim = c(13, 90), ylim = c(0, 1000)) +
  geom_point(alpha = 1/20,
             position = position_jitter(h = 0),
             color = 'orange') +
  stat_summary(fun.y = mean, geom = "line") +
  stat_summary(fun.y = quantile, fun.args = list(probs = .1), geom = "line", color = "red", linetype = 2) +
  stat_summary(fun.y = quantile, fun.args = list(probs = .5), geom = "line", color = "red", linetype = 2) +
  stat_summary(fun.y = quantile, fun.args = list(probs = .9), geom = "line", color = "red", linetype = 2) 
  
```

#### What are some of your observations of the plot?
Response:
plot of them are almost same.
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
with(pf, cor.test(age, friend_count, method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, pf$age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

```{r}
with(subset(pf, age <= 70), cor.test(age, friend_count), method = 'spearman')
```
## Create Scatterplots
Notes:

```{r}

# Create a scatterplot of likes_received (y)
# vs. www_likes_received (x). Use any of the
# techniques that you've learned so far to
# modify the plot.

# ENTER ALL OF YOUR CODE TO CREATE THE PLOT BELOW THIS LINE.
# ===========================================================
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point() +
  scale_x_log10()
  
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
with(pf, cor.test(www_likes_received, likes_received))
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
#install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

# Create a scatterplot of temperature (Temp)
# vs. months (Month).

# ENTER ALL OF YOUR CODE TO CREATE THE PLOT BELOW THIS LINE.
# ===========================================================
library(alr3)
data("Mitchell")
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point()

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
0
b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
with(Mitchell, cor.test(Month, Temp))
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

summary(Mitchell$Month)
range(Mitchell$Month)

ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point()+
  scale_x_continuous(breaks=seq(0, 203, 12))
  
```

***

### A New Perspective

What do you notice?
Response: there are some rule, like sin(),cos() function.

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age ) +
  geom_line()

head(pf.fc_by_age, 10)
pf.fc_by_age[17:19, ]

# Create a new variable, 'age_with_months', in the 'pf' data frame.
# Be sure to save the variable in the data frame rather than creating
# a separate, stand-alone variable. You will need to use the variables
# 'age' and 'dob_month' to create the variable 'age_with_months'.

# Assume the reference date for calculating age is December 31, 2013.

# This programming assignment WILL BE automatically graded. For
# this exercise, you need only create the 'age_with_months' variable;
# no further processing of the data frame is necessary.

# ENTER YOUR CODE BELOW THIS LINE
# ========================================================================

pf$age_with_months = pf$age + (12 - pf$dob_month) / 12

```

***

### Age with Months Means

```{r Age with Months Means}
# Create a new data frame called
# pf.fc_by_age_months that contains
# the mean friend count, the median friend
# count, and the number of users in each
# group of age_with_months. The rows of the
# data framed should be arranged in increasing
# order by the age_with_months variable.

# For example, the first two rows of the resulting
# data frame would look something like...

# age_with_months  friend_count_mean	friend_count_median	n
#              13            275.0000                   275 2
#        13.25000            133.2000                   101 11

# See the Instructor Notes for two hints if you get stuck.
# This programming assignment will automatically be graded.

suppressMessages(library(dplyr))

# ENTER YOUR CODE BELOW THIS LINE
# ========================================================================


pf.fc_by_age_months = pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
           friend_count_median = median(friend_count),
           n = n()) %>%
  arrange(age_with_months)

head(pf.fc_by_age_months)
```
```{r Age with Months Means_alternate method}
age_with_months_groups <- group_by(pf, age_with_months)
pf.fc_by_age_months2 <- summarise(age_with_months_groups,
                          friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n())
pf.fc_by_age_months2 <- arrange(pf.fc_by_age_months2, age_with_months)
head(pf.fc_by_age_months2)
```



Programming Assignment
```{r Programming Assignment}

# Create a new line plot showing friend_count_mean versus the new variable,
# age_with_months. Be sure to use the correct data frame (the one you created
# in the last exercise) AND subset the data to investigate users with ages less
# than 71.

# ENTER YOUR CODE BELOW THIS LINE.
# ===============================================================
ggplot(aes(x = age_with_months, 
           y = friend_count_mean), 
       data = subset(pf.fc_by_age_months, age_with_months <= 71)) +
  geom_line()

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(aes(x = age_with_months, 
           y = friend_count_mean), 
       data = subset(pf.fc_by_age_months, age_with_months <= 71)) +
  geom_line()

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
p1 = ggplot(aes(x = age, y = friend_count_mean), 
       data = subset(pf.fc_by_age, age < 71)) +
  geom_line() +
  geom_smooth()

p2 = ggplot(aes(x = age_with_months, 
           y = friend_count_mean), 
       data = subset(pf.fc_by_age_months, age_with_months <= 71)) +
  geom_line() +
  geom_smooth()

p3 = ggplot(aes(x = round(age / 5) * 5, y = friend_count), 
       data = subset(pf, age < 71)) +
  stat_summary(fun.y = mean, geom = "line", color = "red", linetype = 2)

library(gridExtra)
grid.arrange(p2, p1, p3, ncol = 1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:
1. scatter
2. scatter with conditional limits
3.geom_line()
4.stat_summary()
5.correlation
6. geom_smooth()

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

